MSD panels 1, 2 and 3 Explant Sup

### 2016-08-23 MSD_panels_1_2_3_HVE_sup_analysis.Rmd
adjusted plot sizes for HTML

HVE_all_panels$Assay <-recode(HVE_all_panels$Assay,
                                      "IFN-α2a" = paste("IFN-\U03B1","2a", sep = ""),
                                      "IL-1α" = "IL-1\U03B1",
                                      "MIP-1α"="MIP-1\U03B1",
                                      "TNF-α" = "TNF-\U03B1",
                                      "MIP-3α" = "MIP-3\U03B1",
                                      "MIP-1β" = "MIP-1\U03B2",
                                      "IL-1β" = "IL-1\U03B2",
                                      "IFN-γ" = "IFNg")

@@

```{r checking detection range, echo=FALSE, message = FALSE, warning = FALSE}

@@

```{r  individual analyte plots , echo=FALSE, message = FALSE, warning = FALSE}

ggplot(avgConc_HVE_all_panels_noStds_1to2_noBelow_fullSet, aes(x = Timepoint, y = avgEstConc))+
   geom_point(aes(color = Donor), alpha = 0.75, size = 2)+
  scale_y_log10()+
   labs( y = "Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))

>>>>

HVE_all_panels$Assay <-recode(HVE_all_panels$Assay,
                                      "IFN-α2a" = paste("IFN-\U03B1","2a", sep = ""),
                                      "IL-1α" = "IL-1\U03B1",
                                      "MIP-1α"="MIP-1\U03B1",
                                      "TNF-α" = "TNF-\U03B1",
                                      "MIP-3α" = "MIP-3\U03B1",
                                      "MIP-1β" = "MIP-1\U03B2",
                                      "IL-1β" = "IL-1\U03B2",
                                      "IFN-γ" = "IFNg",
                              "MIG/CXCL9" = "MIG")

@@

```{r checking detection range,fig.height = 6, fig.width = 10, echo=FALSE, message = FALSE, warning = FALSE}

@@

```{r  individual analyte plots,fig.width = 8, fig.height= 13 , echo=FALSE, message = FALSE, warning = FALSE}

ggplot(avgConc_HVE_all_panels_noStds_1to2_noBelow_fullSet, aes(x = Timepoint, y = avgEstConc))+
   geom_point(aes(color = Donor), alpha = 0.75, size = 3)+
  scale_y_log10()+
   labs( y = "Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))

### 2016-08-23 MSD_panels_1_2_3_explant_sup_analysis.Rmd
adjusted plot sizes for HTML

#fixing the greek letters!!
explant_all_panels$Assay <-recode(explant_all_panels$Assay,
                                      "IFN-α2a" = paste("IFN-\U03B1","2a", sep = ""),
                                      "IL-1α" = "IL-1\U03B1",
                                      "MIP-1α"="MIP-1\U03B1",
                                      "TNF-α" = "TNF-\U03B1",
                                      "MIP-3α" = "MIP-3\U03B1",
                                      "MIP-1β" = "MIP-1\U03B2",
                                      "IL-1β" = "IL-1\U03B2",
                                      "IFN-γ" = "IFNg")

@@

```{r checking detection range, echo=FALSE, message = FALSE, warning = FALSE}

@@

ggplot(explant_all_panels_noStds_NumInEach, aes(x = Assay, y=Number_of_Samples))+
         geom_point(aes(color = Detection.Range),size = 2)+
  theme(axis.text.x = element_text(angle=25, size = 7))+
  labs(y = "Number of Samples", x = "Analyte")+
  facet_wrap(~Panel, scales = "free")+
  ggtitle("Number of Samples in each Detection Range per Analyte")

@@

We did a 1:5 dilution of the samples so I multiplied the concentrations by 5 to get an estimate of the stock suparnatent concentration. Black points show the means.

@@

```{r  individual analyte plots, echo=FALSE, message = FALSE, warning = FALSE}

ggplot(avgConc_explant_all_panels_noStds_noBelow_fullSet, aes(x = Timepoint, y = avgEstConc))+
   geom_point(aes(color = Donor),position = position_swarm(0.07), alpha = 0.75, size = 1.5)+
  scale_y_log10()+
   labs( y = "Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))

>>>>

#fixing the greek letters!!
explant_all_panels$Assay <-recode(explant_all_panels$Assay,
                                      "IFN-α2a" = paste("IFN-\U03B1","2a", sep = ""),
                                      "IL-1α" = "IL-1\U03B1",
                                      "MIP-1α"="MIP-1\U03B1",
                                      "TNF-α" = "TNF-\U03B1",
                                      "MIP-3α" = "MIP-3\U03B1",
                                      "MIP-1β" = "MIP-1\U03B2",
                                      "IL-1β" = "IL-1\U03B2",
                                      "IFN-γ" = "IFNg",
                                  "MIG/CXCL9" = "MIG")

@@

```{r checking detection range,fig.height = 5, fig.width = 10, echo=FALSE, message = FALSE, warning = FALSE}

@@

ggplot(explant_all_panels_noStds_NumInEach, aes(x = Assay, y=Number_of_Samples))+
         geom_point(aes(color = Detection.Range),size = 2)+
  theme(axis.text.x = element_text(angle=25, size = 8))+
  labs(y = "Number of Samples", x = "Analyte")+
  facet_wrap(~Panel, scales = "free")+
  ggtitle("Number of Samples in each Detection Range per Analyte")

@@

We did a 1:5 dilution of the samples so I multiplied the concentrations by 5 to get an estimate of the stock suparnatent concentration.

@@

```{r  individual analyte plots, fig.width = 8, fig.height= 13, echo=FALSE}

ggplot(avgConc_explant_all_panels_noStds_noBelow_fullSet, aes(x = Timepoint, y = avgEstConc))+
   geom_point(aes(color = Donor),position = position_swarm(0.1), alpha = 0.75, size = 3)+
  scale_y_log10()+
   labs( y = "Estimated Stock Concentration pg/ml")+
   facet_grid(Assay~Virus, scales = "free_x")+
   theme(axis.text.x = element_text(size = 11))
